\begin{thebibliography}{99}
\bibitem{virtualbox} VirtualBox 
\url{https://www.virtualbox.org/}
\bibitem{virtual_beginner} 仮想化入門\ 
\url{http://www.plathome.co.jp/solution/virtualserver/introduction/}
\bibitem{virtual_taizen} 浅見直樹 日経BP社 
「仮想化大全」 p14-17
\bibitem{vsphere} vSphere
\url{http://www.vmware.com/jp/products/vsphere}
\bibitem{xenserver} XenServer
\url{http://www.citrix.co.jp/products/xenserver/xenserver.html}
\bibitem{hyper-v} Hyper-V
\url{http://www.microsoft.com/ja-jp/server-cloud/windows-server/hyper-v.aspx}
\bibitem{xen} Xen
\url{http://xenproject.org/}
\bibitem{kvm} KVM
\url{http://www.linux-kvm.org/page/Main_Page}
\bibitem{cloud_computing} IT 用語辞典\ 
\url{http://e-words.jp/}
\bibitem{azure} Azure\ 
\url{http://azure.microsoft.com/ja-jp/}
\bibitem{vmotion} VMware Inc. VMware vSPhere 5.1 vMotion
Architecture, Performance, and Best Practices. TECHINICAL WHITE PAPER, 2012.
\bibitem{hyper-v_live} Hyper-V のライブマイグレーションの説明\\
\url{http://technet.microsoft.com/ja-jp/library/hh831435.aspx}
\bibitem{livemigration} Hyper-V 2.0 のライブ・ライブマイグレーションの基礎知識\\
\url{http://www.atmarkit.co.jp/ait/articles/0912/16/news102.html}
\bibitem{xenserver_migration} Storage XenMotion: 
Live Storage Migration with Citrix XenServer
\bibitem{precopy} Christopher Clark, Keir Fraser, Steven Hand, Jacob gorm Hansen,
Eric Jul, Christian Limpach, Ian Pratt and Andrew Warfield. Live migration of virtual machines,
NSDI'05 Proceedings of the 2nd conference on Symposium on Networked Systems Design \& 
Implementation - Volume 2, Pages 273-286 , 2005.
\bibitem{sharing} Carl A. Waldspurger. Memory Resource Management in VMware ESX Server,
Fifth Symposium on Operating Systems Design and Implementation (OSDI ’02), 
Pages 181-194, Dec. 2002.
\bibitem{disco} Edouard Bugnion, Scott Devine, Kinshuk Govil, and Mendel Rosenblum. 
“Disco: Running Commodity Oper- ating Systems on Scalable Multiprocessors,
” ACM Trans- actions on Computer Systems, 15(4), November 1997.
\bibitem{compare-by-hash} Val Henson. An analysis of compare-by-hash.
In HotOS, pages 13–18, 2003.
\bibitem{post-copy} Michael R. Hines and Kartik Gopalan. 
Post-copy based live virtual machine mi- gration using adaptive pre-paging and 
dynamic self-ballooning. 
In Proceedings of the 2009 ACM SIGPLAN/SIGOPS international conference on 
Virtual execution environments, VEE ’09, pp. 51–60, New York, NY, USA, 2009. ACM.
\bibitem{sonic} Akane Koto, Hiroshi Yamada, Kei Ohmura, and Kenji Kono Keio University,
2NTT Software Innovation Center. In Proceeding of
APSys '12 Proceedings of the Third ACM SIGOPS Asia-Pacific conference on Systems, 
Pages 7-7 
\bibitem{thesis_koto} Akane Koto. オペレーティングシステムのメモリ情報を考慮した
仮想マシンマイグレーション高速化手法．Graduation thesis. 2012.
\bibitem{feasibility} Jacob Faber, Kloster Jesper Kristensen, and Arne Mejlholm.
On the Feasibility of Memory Sharing. Master's thesis, Aalborg University, June 2006.
\bibitem{g-compare-by-hash} Val Henson. Guidelines for Using Compare-by-hash. 2005.
\end{thebibliography}
